A Type System for String Sanitation\\Implemented Inside a Python

### 2014-08-06 sanitation-psp14/sanitation-psp14-short.tex
Fixed some refs

\begin{thm}{Input Sanitation Correctness of $\lambdas$}\label{thm:scorrect}
  If $\sctx \vdash S : \stringin{r}$ then either (a) $S \sreduces \rstr{s}$ for $s \in \lang{r}$
  or (b) $S \err$.
\end{thm}
\begin{proof}
  We may actually want a proof here.
\end{proof}

@@

  By theorem \ref{tcorrect}, $P \sreduces \tstr{s}$ implies that $S \sreduces \strin{s}$.
  By theorem \ref{scorrect}, this together with the assumption that $S$ is well-typed implies that $s \in \lang{r}$.

>>>>

\begin{thm}{Input Sanitation Correctness of $\lambdas$.}\label{thm:scorrect}
  If $\sctx \vdash S : \stringin{r}$ then either (a) $S \sreduces \rstr{s}$ for $s \in \lang{r}$
  or (b) $S \err$.
\end{thm}
\begin{proof}
  We may actually want to present this proof.
\end{proof}

@@

  By theorem \ref{thm:tcorrect}, $P \sreduces \tstr{s}$ implies that $S \sreduces \strin{s}$.
  By theorem \ref{thm:scorrect}, this together with the assumption that $S$ is well-typed implies that $s \in \lang{r}$.
